On Secure Delegation of SampBQP with a Classical Client

### 2020-02-02 bqp.tex
Write proofs of blind BQP

\begin{algorithm}
	\caption{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	\begin{algorithmic}[1]
		\State Let $\lambda$ be the security parameter.
		\State Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda)$ to get $pk, sk$.
		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\State The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ to the prover
		\State The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\State The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates
		\State The verifier decodes the measurement results
		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{algorithmic}
\end{algorithm}

@@

\begin{thm}
	\protoref{BlindBQP} has negligible completeness
\end{thm}
\begin{proof}
	\href{http://jwilson.coe.uga.edu/EMT668/EMAT6680.F99/Challen/proof/proof.html}{Well, we'll pretend it's true...}
\end{proof}

\begin{thm}
	\protoref{BlindBQP} has negligible soundness
\end{thm}
\begin{proof}
	\href{http://jwilson.coe.uga.edu/EMT668/EMAT6680.F99/Challen/proof/proof.html}{It sounds good, so it must be true.}
\end{proof}

\begin{thm}
	\protoref{BlindBQP} is IND-CPA
\end{thm}
\begin{proof}
	\href{http://jwilson.coe.uga.edu/EMT668/EMAT6680.F99/Challen/proof/proof.html}{I have this gut feeling.}
\end{proof}

>>>>

\begin{algorithm}
	\caption{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	\begin{algorithmic}[1]
		\State Let $\lambda$ be the security parameter.
		\State Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda)$ to get $pk, sk$.
		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\State The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
		\State The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\State The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates
		\State The verifier decodes the measurement results
		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{algorithmic}
\end{algorithm}

@@

\begin{thm}
	\protoref{BlindBQP} has negligible completeness
\end{thm}
\begin{proof}
	Based on the correctness of $\mathsf{QHE}$, the verifier would successfully decode $\cF(c)$ with overwhelming probability.
	The subsequent underlying QMA check also has overwhelming probability of acceptance.
\end{proof}

\begin{thm}
	\protoref{BlindBQP} has negligible soundness
\end{thm}
\begin{proof}
	The verifier's actions is equivalent to first decoding the prover's message then measuring it.

	Suppose the prover's message decodes to some $\rho$. Since it is a quantum state, the soundness of the underlying $\QMA$ instance can be used.

	That is, there doesn't exists a valid certificate $\rho$ that has non-negligible probability of acceptance.
\end{proof}

\begin{thm}
	\protoref{BlindBQP} is IND-CPA
\end{thm}
\begin{proof}
	The only thing the prover learns is $c$ and $pk$, so this follows directly from $\mathsf{QHE}$'s security.
\end{proof}
